\chapter{Discussion}
This section interprets the numerical results in relation to the main goal of the thesis: to test whether numerical optimization can identify favorable parameter regimes in interacting quantum-dot-superconductor chains that support Majorana-like low-energy physics and useful braiding behavior. It also discusses the implications of extending the braiding analysis beyond the ground-state manifold.

\section{Parameter Optimization Scheme}
For a simple two-dot system, the optimizer managed to approach the analytically known sweet spot, which provides a reassuring sanity check. In the non-interacting case, the gradient-based search found a parameter regime that matches the known sweet spot up to a numerical tolerance of approximately $10^{-3}$. This is a strong indication that the optimization procedure is working correctly, at least in the non-interacting limit.

For weakly interacting two-dot systems, the optimizer found parameter sets that are also close to the expected interacting sweet-spot conditions, where the ground-state degeneracy should be preserved. In particular, the optimized onsite energies remain close to $\epsilon_1,\epsilon_2 \approx -U/2$, with $\Delta \sim t$. This is consistent with the known interacting sweet-spot condition for two-dot systems, and suggests that the optimization is correctly identifying parameter regimes that satisfy the chosen Majorana-based criteria in the presence of weak interactions. For stronger interactions, the optimizer had more difficulty finding low-loss configurations. It also tended to push $\Delta > t$, while the relation between $\epsilon_i$ and $U$ remained close to the expected sweet-spot condition. This trend is consistent with the constrained parameter space becoming less able to maintain even--odd degeneracy across the relevant energy levels when the interaction strength grows relative to the fixed hopping scale. However, the present searches cannot separate such a physical limitation from the increased difficulty of optimizing a more complicated loss landscape.

Beyond the two-dot sweet spot, the analytical solution rapidly becomes more complicated. Without assuming symmetry or homogeneity, the number of parameters grows with the system size, and solving the sweet-spot conditions analytically becomes increasingly difficult. This makes numerical optimization a well-motivated approach for larger systems. For the three- and four-dot systems, the optimizer found parameter regimes that are not close to a simple homogeneous sweet-spot picture. Instead, the optimized parameters show a clear trend toward strong inhomogeneity, with large-magnitude onsite potentials in the middle of the chain and, for the four-dot system, enhanced pairing amplitudes near the center. This suggests that nontrivial inhomogeneous configurations can satisfy the chosen Majorana-based criteria, but it does not by itself establish why those profiles are favorable.

The parameter searches across all system sizes show that strong interactions make it substantially harder to find low-loss configurations. This is consistent with the expectation that strong interactions can destabilize Majorana-like physics, but optimization limitations cannot be excluded. Distinguishing these explanations would require more extensive searches or controlled comparisons of the loss landscape at different interaction strengths.
However, at lower interaction strengths, especially in the three-dot system, the optimizer was able to find favorable low-loss configurations. This indicates that weakly interacting parameter regimes can satisfy the combined spectral and local criteria used in the optimization.
For the four-dot system, the optimizer struggled more to find low-loss configurations even at weak interactions. This could reflect limitations of the optimization strategy, but it could also indicate that the parameter space becomes more complex and potentially more constrained as the system size increases. Since the optimization budget was kept fixed across all system sizes, the larger systems may not have been explored as thoroughly as the smaller ones. It would therefore be interesting to test whether increasing the number of iterations or using a more global search strategy could help the optimizer find better configurations for the four-dot system, especially in the weak-interaction regime.

One of the more interesting findings for chains longer than two dots was the emergence of large-magnitude onsite potentials in the middle of the chain. This was not expected from the simple sweet-spot picture. The resulting interior detuning is correlated with favorable edge-localization diagnostics and is consistent with suppressing bulk Majorana weight. A controlled scan of the interior potentials would be needed to establish whether this is the mechanism responsible. Subject to that qualification, the result motivates studying controlled inhomogeneity as a possible design parameter rather than treating it only as an imperfection.

\section{Braiding Analysis}
The braiding results are mainly split into two parts. The low-energy benchmark compares the ideal four-Majorana reference model with projected microscopic junction and local-operator models. The sector-resolved analysis then compares an energy-level Majorana baseline with direct and block-matched projected local-operator constructions.

The main difference between the two constructions is what they test. The energy-level construction tests whether Majorana operators built from paired eigenstates define an internally consistent effective exchange channel. The local-operator constructions instead test whether braids built from projected endpoint operators accurately execute targets defined from those local operators. In the sector-resolved results, each construction is compared with its own target. The reported self-target errors can therefore reveal sector dependence within a construction, but they do not by themselves determine whether the local constructions reproduce the energy-level exchange channel. Establishing that stronger comparison requires evaluating all constructions against a common target.

The first part of the analysis tests whether braiding can be performed in the ground-state manifold using the Majorana modes generated by the optimized parameters. Based on the post-optimization results, the optimized $U=0.1$ three-dot system was selected as the most promising candidate for the interacting braiding analysis. The results show that the ground-state manifold is well isolated, and that the projected junction operators closely match the ideal Majorana bilinears. This is a strong indication that the optimized parameters support Majorana-like physics in the ground-state manifold, and that the braiding protocol can be successfully implemented within this projected model.

After verifying the braid in the ground-state manifold, we extended the analysis to higher energy sectors and compared the interaction strengths $\frac{U}{t}=0.0,0.1,0.5,1.0,2.0$. This was done in three parts. First, the energy-level Majorana baseline tested whether paired eigenstates define a stable exchange channel in each sector. Second, the direct projected local-operator construction tested whether a microscopic endpoint operator can perform its corresponding self-target braid in the same sectors. Finally, the block-matched local-operator construction resolved the internal labelled blocks of each sector and fitted the local operator independently within them.

These results are shown in \cref{fig:ideal_operator_interaction_regimes,fig:projected_operator_interaction_regimes,fig:matched_operator_interaction_regimes,fig:mean_braid_errors}. The reported self-target braids work well across all sectors for the non-interacting and weakly interacting configurations. This is consistent with the optimization scheme favoring even--odd degeneracy across the spectrum while also favoring gaps between neighboring parity pairs.

The energy-level Majorana baseline is stable for most tested interaction strengths, but the $U=1.0$ configuration is strongly sector dependent. Some of its sectors braid accurately, while others fail by several orders of magnitude. Since the $U=2.0$ energy-level baseline performs much better, interaction strength alone does not explain the ordering of the selected configurations. The irregular $U=1.0$ result may reflect its particular optimized parameters, non-monotonic interaction effects, or both. It remains possible that a better $U=1.0$ minimum exists elsewhere in the optimization landscape.

The direct and block-matched local-operator constructions show a stronger dependence of their self-target errors on both interaction strength and sector. The $U=0.5$ case, which remains in the low-deviation regime for the energy-level Majorana baseline, moves into the intermediate-deviation regime for both local constructions. The ground-state sector is nevertheless among the lower-error sectors in most cases. Within the self-target comparison used here, the block-matched local-operator braid gives almost the same deviations as the direct local-operator braid. Resolving the internal block structure therefore does not by itself remove the observed self-target sensitivity, although this comparison does not establish how either local construction agrees with the energy-level target.


\section{Limitations and Outlook}

The main limitation of the present study is that the optimization procedure does not locate exact sweet spots; it finds numerically favorable minima of the chosen loss function. In a complicated loss landscape, a low loss may represent a local minimum even when a better solution exists elsewhere. Moreover, the spectral, charge, and Majorana-polarization diagnostics are also components of the optimization objective. Their favorable values confirm that the optimizer satisfies its intended criteria, but they are not fully independent validation of the resulting configurations. The low-energy microscopic-junction braid provides a more independent test, since it is not directly optimized. There is also no direct correspondence between the numerical value of the loss and the expected error of a later observable. The results should therefore be interpreted as evidence for approximate Majorana-like behavior within the tested models, not as proof of exact topological protection.

A second limitation is that the present braiding analysis is still highly controlled. The clean agreement found in the lowest manifold relies on projection to a small low-energy space and on an idealized, disorder-free setting. The study does not yet include disorder, quasiparticle poisoning, nonadiabatic driving errors, or explicit coupling to thermal environments. Those effects are precisely the kinds of ingredients that would determine whether the optimized configurations remain useful in a more realistic device-level setting.

Within the controlled sector-resolved projected models, a potentially useful finding is that the braiding protocol can also be implemented in higher-energy sectors. For configurations with a stable exchange channel, the self-target results are relatively insensitive to the selected sector. The strongly sector-dependent $U=1.0$ result shows that this behavior is not guaranteed and may depend strongly on the optimized parameter set. Whether such higher-energy sectors can be prepared and manipulated in a realistic device remains an open question. The repeated interior detuning in the optimized parameters also motivates a controlled study of whether inhomogeneous onsite potentials can suppress bulk Majorana weight and improve edge localization.
