\documentclass[UKenglish]{uiomasterthesis}
\usepackage[utf8]{inputenc}
\usepackage[english]{uiomasterfp}
\usepackage{hyperref}
\hypersetup{pdfborder=0 0 0}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage[none]{hyphenat}
\usepackage{xcolor}
% \usepackage{cite}
\usepackage{lipsum}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{physics}
\usepackage{textgreek}
\usepackage{unicode-math}
\usepackage{subfigure}
\usepackage{graphicx}
\graphicspath{{/home/Hishem/repos/Special_curriculum/Figures/}{/home/Hishem/repos/Special_curriculum/External_Figs/}}
\usepackage{subcaption}  % in the preamble
\usepackage{textgreek}
\usepackage{xcolor}
\usepackage[backend=biber,style=numeric-comp]{biblatex}
\usepackage[english]{babel}
\usepackage[capitalise]{cleveref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{array}

\addbibresource{refs.bib}
 \title{Numerical Optimization and Braiding of Poor Man's Majorana Chains}
 \subtitle{Interactions, Projected Exchange, and Higher-Energy Sectors}

 \author{Hishem Kløvnes}

\begin{document}
\uiomasterfp[color={blue}, date={Spring 2026}, dept={Computational Science: Physics}, fac={Faculty of Mathematics and Natural Sciences}, kind={Master's Thesis Spring 2026}, long, supervisors={Viktor Svensson\\Morten Hjorth-Jensen}]



% \begin{center}
%     \vspace*{\fill}
%     \textbf{\textquoteleft electron-phonon interaction is a highly retarded attractive interaction\textquoteright}\\
%     \quad \quad \textemdash\ \textit{P. Coleman, 2015\\
%     -Introduction to Many-Body Physics, p.490}
%     \vspace*{\fill}

% \end{center}


\chapter*{Declaration of AI Use}
In this thesis, GitHub Copilot and OpenAI's Codex in VS Code were used for the following purposes:
\begin{itemize}
    \item Spell-checking, grammar, and flow, manually verified by me.
    \item Assistance with \LaTeX\ formatting and syntax, including missing references and the generation of tables and figures, manually verified by me.
    \item Creation of helper functions for plotting.
    \item Assistance in debugging code and \LaTeX\ errors.
    \item Help with spotting errors, inconsistencies, and redundancies in the text, manually verified and corrected by me.
\end{itemize}

\chapter*{Acknowledgements}

There have been plenty of ups and downs during this project, and I would like to thank the people who have helped me along the way. First, I would like to thank my supervisors, Viktor Svensson and Morten Hjorth-Jensen, for their time, guidance, and support throughout the project.

I would like to thank my family, my father, mother, Shadia, and Matilde, for their support both during my studies and throughout the years leading up to this moment. I am also grateful to them for sparking my interest in science and mathematics at a young age, and for always encouraging me to pursue my interests.

I would also like to thank my friends for helping me unwind and relax when I needed to. I also want to thank Madelén for her unconditional support during both good and stressful times. Lastly, I would like to thank my peers and colleagues for both serious and lighthearted conversations.

This has been a long journey, and I am grateful for all the help and support I have received along the way.


\begin{abstract}
Majorana zero modes are interesting for quantum computation because they can store information non-locally, making the encoded state less sensitive to local disturbances. In realistic devices, however, creating and controlling such modes is difficult. Poor Man's Majorana systems use short chains of quantum dots coupled through superconducting pairing to mimic some of the physics of a Kitaev chain in a smaller and more tunable platform. Because these systems are finite and can be affected by interactions, it is not obvious which parameters give useful Majorana-like behavior or whether the resulting states support the expected exchange operation.

This thesis studies this problem using numerical optimization. Spinless two-, three-, and four-dot chains are optimized at fixed hopping and interaction strengths by tuning onsite energies and pairing amplitudes. The optimized systems are evaluated using energy degeneracy, excitation gaps, local charge differences, and Majorana-polarization diagnostics. The most promising configurations are then used in a three-subsystem braiding geometry, where the resulting exchange operation is tested using numerical adiabatic transport.

The optimization reproduces the known non-interacting two-dot sweet spot and finds more inhomogeneous parameter profiles for longer chains. Among the tested interacting systems, the weakly interacting three-dot chain gives the best overall balance of small ground-state splitting, large excitation gap, edge-localized Majorana polarization, and suppressed bulk polarization. In the lowest projected manifold, this configuration reproduces the expected Majorana exchange with high accuracy.

The braiding analysis was also extended to higher energy sectors. For non-interacting and weakly interacting configurations, the sector-resolved self-target braid tests remain accurate across the tested sectors. However, higher-dimensional sectors can contain several internal blocks with different exchange orientations, meaning that the full sector does not necessarily implement one uniform logical gate. These results show that optimized finite quantum-dot chains can reproduce Majorana-like exchange in controlled projected models, and that braiding beyond a known low-energy block requires additional control over which sector or block is occupied.

    % Poor Man's Majorana (PMM) models provide a compact and tunable platform for quantum computation, but their finite size and sensitivity to interactions make it difficult to identify useful parameter regimes. This thesis investigates whether interacting quantum-dot chains can be numerically optimized to exhibit favorable Majorana-like properties and whether the resulting configurations support the expected Majorana exchange within projected braiding models.

% Spinless two-, three-, and four-dot PMM chains are studied at fixed hopping and interaction strengths. The onsite energies and pairing amplitudes are optimized using a customized loss function that combines typical Majorana diagnostics. Selected configurations are then used as building blocks for a three-subsystem braiding geometry. The resulting geometric braid unitaries are computed using Kato transport and compared across ideal Majorana, projected microscopic-junction, energy-level, projected local-operator, and block-matched local-operator constructions.

% The optimization reproduces the known non-interacting two-dot sweet spot and finds increasingly inhomogeneous parameter profiles for longer chains. Among the tested interacting configurations, the three-dot system at $\frac{U}{t} = 0.1$ provides a strong overall balance of spectral near-degeneracy, excitation gap, edge-localized Majorana polarization, and suppressed bulk polarization. Within its lowest projected manifold, the projected microscopic junction braid reproduces the expected Majorana exchange with high accuracy. Sector-resolved self-target scans remain accurate across the tested sectors for the non-interacting and weakly interacting configurations, while the selected stronger-interaction local-operator constructions show greater sector dependence.


% The block-matching analysis shows that projected local operators can be represented essentially exactly within the energy-level Majorana basis. However, different internal blocks of the same higher-dimensional energy sector can follow opposite exchange orientations. A complete higher-dimensional sector therefore does not necessarily implement one uniform logical gate. These results demonstrate useful Majorana-like exchange within controlled finite projected models, while also showing that extending braiding beyond a known low-energy block requires control of the occupied block and a common-target comparison between local and energy-level exchange channels.
\end{abstract}

\tableofcontents
\newpage
\include{introduction}
\newpage
\include{theory_2}
% \newpage
\include{method_2}
% \newpage
% \include{method}
% \newpage
\include{results_2}
% \include{results}
% \newpage
\include{discussion}
% \newpage
\include{conclusion}
% \newpage
\appendix
\include{appendix}

\backmatter{}
\printbibliography{}

\end{document}

