\chapter{Method}

This chapter describes the methods used to optimize the Majorana modes in the junction setup and to analyze their properties. We first discuss the parameter optimization process, including the model parameterization, loss function design based on Majorana criteria, and the optimization strategy. Next, we detail the post-optimization analysis of the setup, covering Hamiltonian reconstruction, parity classification, and various diagnostics. Finally, we describe the braiding protocol implemented in an effective Majorana model and how we validate the results using gate-validation checks.

\section{Numerical PMM Hamiltonian and Basis}
The numerical calculations are built from the spinless $n$-dot PMM Hamiltonian introduced in the theory chapter. This section specifies how that model is represented in the code: which Hamiltonian is diagonalized, which basis is used, how the fermionic operators are constructed, and how the model parameters are organized before optimization and braiding calculations. The goal here is not to rederive the PMM model, but to define the concrete numerical object used throughout the rest of the method chapter.

\subsection{Single-Chain Hamiltonian}
For a single $n$-dot PMM chain, the Hamiltonian used in the optimization and diagnostic calculations is
\begin{equation}
H_{\mathrm{PMM}}
=
\sum_{i=1}^{n} \epsilon_i n_i
+ \sum_{i=1}^{n-1}
\left[
-t_i\left(c_i^\dagger c_{i+1}+c_{i+1}^\dagger c_i\right)
+\Delta_i\left(c_i c_{i+1}+c_{i+1}^\dagger c_i^\dagger\right)
+U_i n_i n_{i+1}
\right].
\label{eq:method_pmm_hamiltonian}
\end{equation}
Here $c_i^\dagger$ and $c_i$ create and annihilate a spinless fermion on dot $i$, and $n_i=c_i^\dagger c_i$ is the corresponding number operator. The onsite energies $\epsilon_i$ play the role of local chemical potentials, $t_i$ are elastic cotunneling amplitudes, $\Delta_i$ are crossed-Andreev pairing amplitudes, and $U_i$ are nearest-neighbor density-density interaction strengths. This is the same operator structure used both when searching for optimized PMM chains and when reconstructing selected chains for later braiding calculations.

\subsection{Many-Body Fock Basis}
All operators are represented in the full many-body Fock basis. For a chain with $n$ dots, a basis state is specified by the occupation pattern
\begin{equation}
\ket{n_1 n_2 \cdots n_n},
\qquad
n_i\in\{0,1\},
\end{equation}
so the Hilbert-space dimension of a single chain is $2^n$. Diagonalizing Eq.~\ref{eq:method_pmm_hamiltonian} in this basis gives the full many-body spectrum and eigenstates. This is important because the diagnostics used later, such as parity classification, charge expectation values, and Majorana-polarization matrix elements, are all many-body quantities.

For braiding calculations, several optimized chains are combined into a larger Hilbert space. If $D$ identical PMM subsystems are used, each containing $n$ dots, the total number of fermionic sites is $N_{\mathrm{tot}}=Dn$ and the full Hilbert-space dimension is $2^{N_{\mathrm{tot}}}$. In the three-arm braiding geometry used later, $D=3$, corresponding to subsystems $A$, $B$, and $C$.

\subsection{Jordan-Wigner Construction of Fermionic Operators}
\label{sec:method-jordan-wigner-construction}
The fermionic creation and annihilation operators must satisfy the canonical anticommutation relations
\begin{equation}
\{c_i,c_j^\dagger\}=\delta_{ij},
\qquad
\{c_i,c_j\}=\{c_i^\dagger,c_j^\dagger\}=0.
\end{equation}
In the code, these operators are constructed with Jordan-Wigner strings. Starting from local spin raising and lowering operators on site $j$, the fermionic operators are represented schematically as
\begin{equation}
c_j^\dagger =
\left[\prod_{k<j}(-\sigma_k^z)\right]\sigma_j^+,
\qquad
c_j =
\left[\prod_{k<j}(-\sigma_k^z)\right]\sigma_j^-.
\label{eq:method_jw_operators}
\end{equation}
The string of $\sigma^z$ operators keeps track of the fermionic sign picked up when operators on different sites are exchanged. This same construction is used for single-chain calculations and for the enlarged three-subsystem Hilbert space. In the latter case, the site ordering fixes the Jordan-Wigner strings across subsystems, ensuring that operators belonging to different PMM chains still anticommute correctly.

Once the creation and annihilation operators have been constructed, the code precomputes the basic operator products needed repeatedly:
\begin{equation}
n_i=c_i^\dagger c_i,\qquad
h_{ij}=c_i^\dagger c_j+c_j^\dagger c_i,\qquad
p_{ij}=c_i^\dagger c_j^\dagger+c_j c_i,\qquad
d_{ij}=n_i n_j .
\end{equation}
These building blocks are then combined with the parameter values in Eq.~\ref{eq:method_pmm_hamiltonian} to assemble the Hamiltonian matrix. 
The same Jordan-Wigner ordering is also used when several PMM chains are embedded into the combined braiding Hilbert space, so that the fermionic operators of different subsystems anticommute correctly. For the three-subsystem geometry, sites are ordered as
$$
A_1, A_2, \ldots, A_n, B_1, B_2, \ldots, B_n, C_1, C_2, \ldots, C_n.
$$
Operators acting on subsystem B therefore carry a Jordan-Wigner string over all sites in subsystem A, while all operators acting on subsystem C carry a string over all sites in both A and B. This ensures that the fermionic algebra is preserved across the entire device, which is crucial for correctly defining the Majorana operators and their braiding properties later on.

\subsection{Parameter Conventions}
The numerical implementation allows each parameter family in Eq.~\ref{eq:method_pmm_hamiltonian} to be fixed, homogeneous, or inhomogeneous. A fixed parameter is held at a prescribed value and is not included in the optimization vector. A homogeneous parameter has the same value on every site or bond, while an inhomogeneous parameter is allowed to vary independently from site to site or bond to bond. This convention makes it possible to compare restricted ans\"atze with more flexible parameter searches using the same Hamiltonian-building routine.

In the main optimization runs used in this thesis, the hopping amplitudes are fixed to $t_i=1$, and the interaction strength is fixed to selected values of $U$. The onsite energies $\epsilon_i$ and pairing amplitudes $\Delta_i$ are optimized. Fixing the hopping scale prevents the optimizer from lowering the loss through a trivial global rescaling of the kinetic energy, and instead forces the search to find nontrivial onsite and pairing profiles for each interaction regime. This also rules out the possibility of blowing up all other parameters in order to suppress the relative effect of interactions, which would be an unphysical way to achieve a low loss in the strongly interacting regime. The optimized parameters are stored in a reduced vector form, where only the free parameters are included. After optimization, the full set of physical parameters is reconstructed by reinserting fixed values and expanding homogeneous parameters as needed.

After optimization, the selected physical parameters are stored and later reloaded for post-optimization diagnostics and braiding calculations. The same parameter convention is also used when constructing the three-subsystem braiding geometry: the optimized single-chain parameters define each subsystem, while additional inter-subsystem couplings are introduced only in the braiding-model sections below.

\section{Parameter Optimization and Loss Function}
The purpose of the optimization is to find parameter regimes where the finite PMM chain has the spectral and local signatures of Majorana-like states. The theory chapter defined the physical criteria; here they are turned into a numerical objective. For each trial parameter vector, the Hamiltonian in Eq.~\ref{eq:method_pmm_hamiltonian} is constructed, diagonalized, separated into parity sectors, and assigned a scalar loss. The optimizer then updates only the free parameters, while fixed parameters are reinserted when the physical Hamiltonian is rebuilt.

\subsection{Optimization Vector and Physical Parameters}
The optimizer does not act directly on a full dictionary of physical parameters. Instead, it acts on a reduced real vector $\theta$ containing only the entries that are not fixed by the chosen parameter configuration. For example, if $t_i$ is fixed and $U_i$ is fixed to a selected interaction strength, then those entries are omitted from $\theta$. If a parameter is homogeneous, only one number is included; if it is inhomogeneous, one number is included for each site or bond.

The reduced vector is converted back into a parameter dictionary before the Hamiltonian is evaluated. Schematically,
\begin{equation}
\theta
\longrightarrow
\{t_i,U_i,\epsilon_i,\Delta_i\}
\longrightarrow
H_{\mathrm{PMM}}(\theta).
\end{equation}
During this conversion, fixed values are reinserted, homogeneous values are expanded across all sites or bonds when needed, and positive couplings such as $t_i$, $U_i$, and $\Delta_i$ are constrained to be non-negative by taking their absolute values. This separation between the optimization vector and the physical parameter dictionary makes it possible to use the same code for different ans\"atze.

In the main optimization runs, the hopping amplitudes are fixed to $t_i=1$, while the interaction strength $U$ is fixed to the value being studied. The remaining parameters, primarily the onsite energies $\epsilon_i$ and pairing amplitudes $\Delta_i$, are optimized. For each system size $n$ and interaction strength $U$, the lowest-loss physical parameter set is stored and later reused in the diagnostic and braiding calculations.

\subsection{Parity Classification Inside the Loss}
For each trial Hamiltonian, the full many-body spectrum is obtained by exact diagonalization. The eigenstates are then classified by the total fermion parity operator,
\begin{equation}
P_{\mathrm{tot}}=\prod_{i=1}^{n}(1-2n_i).
\end{equation}
This gives two ordered energy lists, one in the even sector and one in the odd sector,
\begin{equation}
\{E_k^{(e)}\},
\qquad
\{E_k^{(o)}\}.
\end{equation}
The loss function compares these parity partners level by level. If the diagonalization produces an invalid parity structure, for example if one sector is missing or if the two sectors cannot be paired consistently, the trial point is discarded and the optimizer proceeds to another restart or candidate point.

\subsection{Even-Odd Degeneracy Term}
The first loss contribution penalizes energy splitting between even- and odd-parity partners,
\begin{equation}
\delta_k = \left|E_k^{(e)}-E_k^{(o)}\right|.
\end{equation}
In an ideal non-interacting Kitaev chain at the sweet spot, or in the infinite-length limit, this contribution would vanish because the Majorana zero mode gives an exact even-odd degeneracy. In the finite interacting systems studied here, however, both Majorana overlap and interaction effects can split the parity partners, so this term is included explicitly in the loss function.
These splittings are weighted more strongly at low energy, because the ground-state degeneracy is the most important Majorana signature. In the implementation, the weights decrease from a maximum value for the lowest parity pair to a smaller value for higher levels. The degeneracy contribution therefore has the schematic form
\begin{equation}
\mathcal{L}_{\mathrm{deg}}
=
\sum_{k} w_k \left|E_k^{(e)}-E_k^{(o)}\right|,
\qquad
w_0>w_1>\cdots .
\end{equation}
This term encourages the optimizer to produce an approximately parity-paired spectrum, with particular emphasis on the lowest-energy states.

\subsection{Excitation-Gap Term}
Degeneracy alone is not sufficient: the parity-paired states must also be separated from nearby levels. The second loss contribution penalizes small gaps within the parity-resolved spectra. For adjacent levels, the relevant gap is taken as the smaller of the even-sector and odd-sector spacings,
\begin{equation}
\Delta_k
=
\min\left(
E_{k+1}^{(e)}-E_k^{(e)},
E_{k+1}^{(o)}-E_k^{(o)}
\right).
\end{equation}
Small gaps are penalized using a smooth threshold function,
\begin{equation}
\mathcal{L}_{\mathrm{gap}}
=
\sum_k \tilde{w}_k\,
\mathrm{softplus}
\left(
\Delta_{\mathrm{target}}-\Delta_k
\right),
\end{equation}
where $\Delta_{\mathrm{target}}$ is the desired minimum gap scale, and the softplus function is defined as $\mathrm{softplus}(x) = \log(1 + e^x)$\cite{NIPS2000_44968aec}. This term favors spectra where the relevant parity-paired states are not only close to each other, but also isolated from the rest of the spectrum.

\subsection{Charge and Majorana-Polarization Terms}
The loss also includes local diagnostics that test whether the parity partners resemble Majorana states rather than accidental degeneracies. The charge penalty measures how differently the even and odd partners occupy each site,
\begin{equation}
\mathcal{L}_{Q}
=
\sum_{k}\sum_{j}
\left|
\bra{e_k}n_j\ket{e_k}
-
\bra{o_k}n_j\ket{o_k}
\right|.
\end{equation}
A small value means that the parity partners have similar local charge distributions, consistent with non-local encoding.

The Majorana-polarization penalty compares the site-resolved Majorana-polarization profile with the expected edge-localized pattern. In the target configuration, the polarization is concentrated on the two ends of the chain with opposite sign, while the bulk sites carry little weight. Numerically, the penalty is evaluated from matrix elements of local Majorana operators between the even and odd parity partners. The sign of the target pattern is allowed to flip, since exchanging the labels of the two Majorana components changes the overall sign but not the physical localization pattern.

\subsection{Total Normalized Loss}
The full loss is a weighted sum of the spectral and local contributions. In the implementation, the degeneracy and gap terms are first collected into a single weighted spectral penalty array, after which the charge and Majorana-polarization penalties are added. Written schematically, the implemented loss is
\begin{equation}
\mathcal{L}
=
\frac{
ω_{\mathrm{deg}}\mathcal{L}_{\mathrm{deg}}
+
ω_{\mathrm{gap}}\mathcal{L}_{\mathrm{gap}}
+
\mathcal{L}_{Q}
+
\mathcal{L}_{\mathrm{MP}}
}{
\overline{|E|}+\eta
},
\end{equation}
where $\overline{|E|}$ is the mean absolute energy scale of the spectrum and $\eta$ is a small numerical offset. $ω_{\mathrm{deg}}$ and $ω_{\mathrm{gap}}$ are weight arrays, created to favor the low-energy part of the spectrum, which are the most essential states. The degeneracy and gap contributions contain level-dependent weights that emphasize the low-energy part of the spectrum, where the Majorana signatures are most important.

The normalization by $\overline{|E|}$ makes the spectral part of the loss less sensitive to the overall energy scale of a trial Hamiltonian. However, this normalization is not invariant under a uniform energy shift $H\mapsto H+\alpha\mathbb{1}$, since such a shift changes the absolute energies but leaves gaps and eigenvectors unchanged. In the parametrization used here there is no independent identity-shift parameter, so the optimizer does not explore such shifts directly.

A further limitation is that the same denominator also rescales the charge and Majorana-polarization penalties. These terms are dimensionless eigenvector diagnostics rather than energy penalties, so dividing them by an energy scale can make their contribution smaller when the spectrum becomes larger, even if the local Majorana quality does not improve. This possible bias is partly mitigated by fixing the hopping scale to $t=1$ and fixing $U$ during each optimization run, but the scalar loss should still be interpreted together with the separate spectral and local diagnostics.


\subsection{Search Strategy}
The resulting loss landscape is non-convex, and in practise, we find that the interacting loss landscape is more complicated. The numerical search therefore combines local gradient-based optimization with repeated restarts and basin hopping. Local optimization is performed with Adam. At each iteration, the reduced vector $\theta$ is converted into physical parameters, the Hamiltonian is built and diagonalized, the loss is evaluated within the PyTorch optimization loop and used to update the free parameters with Adam.

Because a single local run can converge to a poor local minimum, the local optimization is repeated from randomly perturbed initial vectors. The lowest-loss result among these restarts is retained as the representative of that region of parameter space. Basin hopping is then used to explore different regions: a random displacement is applied to the current parameter vector, local optimization with restarts is performed again, and the new candidate is accepted if it improves the loss. Candidates with slightly worse loss can also be accepted with a Metropolis probability, allowing the search to escape shallow local minima.

For each pair $(n,U)$, the best configuration found by this procedure is stored together with its loss, parameter configuration, and reconstructed physical parameters. These stored configurations form the input to the post-optimization diagnostics described in the next section.

\section{Post-Optimization Diagnostics}
The optimization procedure returns candidate parameter sets ranked by a scalar loss. 
Since this loss is a soft weighted objective rather than a set of hard constraints, a low value does not by itself prove that the Hamiltonian realizes an ideal Majorana regime. Different loss contributions can trade off against each other, finite weights allow residual even--odd splittings, and the local charge and Majorana-polarization penalties may be small without giving a perfectly isolated ground-state doublet.

For this reason, after optimizing many configurations, the lowest-loss result for each pair $(n,U)$ is selected and analyzed separately. The stored optimized parameters $\Phi_{\mathrm{opt}}(n,U)$ are used to rebuild $H_{\mathrm{PMM}}(\theta_{\mathrm{opt}})$, which is then diagonalized and evaluated using the diagnostics below. This post-optimization step resolves the single scalar loss into physical quantities such as the ground-state splitting, excitation gap, charge difference, and Majorana-polarization profile.

\subsection{Parity-Resolved Spectrum}
Using the parity classification introduced in Sec.~\ref{sec:theory-parity-resolved-spectrum}, the reconstructed Hamiltonian is diagonalized and separated into ordered even- and odd-parity spectra using the total fermion parity operator
\begin{equation}
P_{\mathrm{tot}}=\prod_{i=1}^{n}(1-2n_i).
\end{equation}
For plotting and comparison, all energies are shifted so that the lowest state in either parity sector has energy zero.

The most important scalar spectral diagnostic is the splitting of the lowest even-odd pair,
\begin{equation}
\delta_0 =
\left|
E_0^{(e)}-E_0^{(o)}
\right|.
\label{eq:method_ground_state_splitting}
\end{equation}
The corresponding low-energy gap is defined as
\begin{equation}
\Delta_{\mathrm{gap}}
=
\min\left(E_1^{(e)},E_1^{(o)}\right)
-
\max\left(E_0^{(e)},E_0^{(o)}\right),
\label{eq:method_low_energy_gap}
\end{equation}
after the common ground-state energy shift. This quantity measures the distance from the lowest parity pair to the nearest excited state in either parity sector.

\subsection{Local Charge Difference}
Following the local-distinguishability discussion in Sec.~\ref{sec:theory-local-distinguishability}, the diagnostic routine evaluates the site-resolved charge difference for the lowest parity pair,
\begin{equation}
q_i =
\left|
\bra{e_0}n_i\ket{e_0}
-
\bra{o_0}n_i\ket{o_0}
\right|.
\end{equation}
The total charge difference reported in the results is
\begin{equation}
Q_0=\sum_{i=1}^{n} q_i .
\label{eq:method_charge_difference}
\end{equation}
In the diagnostic figures, the individual $q_i$ values are plotted on top of the Majorana-polarization profile so that charge visibility and spatial localization can be compared site by site.

\subsection{Majorana-Polarization Profile}
Using the Majorana-polarization diagnostic defined in Sec.~\ref{sec:theory-majorana-polarization}, the post-optimization routine computes the lowest-pair profile $M_i$ from matrix elements of local Majorana operators between parity-partner states.

To summarize this profile in the results, two scalar quantities are extracted. The edge polarization is defined as the mean absolute polarization on the two end sites,
\begin{equation}
\overline{|M_{\mathrm{edge}}|}
=
\frac{1}{2}
\left(
|M_1|+|M_n|
\right),
\label{eq:method_edge_polarization}
\end{equation}
while the bulk polarization is defined as the largest absolute value on the interior sites,
\begin{equation}
\max |M_{\mathrm{bulk}}|
=
\max_{2\leq i\leq n-1}|M_i|.
\label{eq:method_bulk_polarization}
\end{equation}
For two-dot systems there are no interior sites, so the bulk contribution is set to zero.

\subsection{Selection for Braiding Calculations}
The post-optimization diagnostics determine which optimized chains are used in the braiding calculations. Since the later sector-resolved braiding analysis tests projected manifolds beyond the lowest parity pair, the selected configurations are not judged only by the ground-state splitting, but also by the excitation gap, charge difference, and Majorana-polarization profile across the relevant low-energy structure.

\section{Effective Majorana Operator Construction}
\label{sec:method-effective-majorana-construction}
% 3.4 Effective Majorana Operator Construction
%   - energy-level Majoranas from even/odd pairs
%   - number of parity pairs included
%   - projected plus/minus components
%   - embedding into three-subsystem Hilbert space with JW strings
%   - normalization and algebra checks
The braiding calculations require explicit matrix representations of the Majorana operators associated with the optimized PMM chains. The theory chapter described why these operators should connect even and odd parity states. Here the focus is narrower: how the operators are constructed from the optimized eigenstates, embedded into the three-subsystem Hilbert space, projected to a chosen low-energy space, and checked before they are used in the braid.

\subsection{Energy-Level Majoranas from Parity Pairs}
For each optimized subsystem, the Hamiltonian is diagonalized and the eigenstates are separated into even and odd parity sectors. The states are then paired by their order in energy. From the $j$th even-odd pair, two parity-changing operators are formed,
\begin{equation}
\gamma_{+,j}
=
\ket{e_j}\bra{o_j}
+
\ket{o_j}\bra{e_j},
\qquad
\gamma_{-,j}
=
i\left(
\ket{e_j}\bra{o_j}
-
\ket{o_j}\bra{e_j}
\right).
\end{equation}
The effective Majorana operators used in the projected calculations are built by summing these contributions over a selected number of parity pairs,
\begin{equation}
\gamma_{+}^{(m)}
=
\sum_{j=0}^{m-1}\gamma_{+,j},
\qquad
\gamma_{-}^{(m)}
=
\sum_{j=0}^{m-1}\gamma_{-,j}.
\label{eq:method_energy_level_majoranas}
\end{equation}
Here $m$ is the number of even-odd pairs included in the operator construction. In the code this is controlled separately from the total projection dimension: the projection dimension determines how much of the full three-subsystem Hilbert space is retained, while $m$ determines how many subsystem parity pairs are used to build the Majorana operator itself.

\subsection{Embedding Into the Three-Subsystem Hilbert Space}
Using the Jordan--Wigner ordering specified in Sec.~\ref{sec:method-jordan-wigner-construction}, subsystem operators are embedded into the full three-subsystem Hilbert space as
\begin{equation}
\gamma_A \mapsto \gamma_A\otimes I_B\otimes I_C,
\end{equation}
\begin{equation}
\gamma_B \mapsto JW_A\otimes \gamma_B\otimes I_C,
\end{equation}
and
\begin{equation}
\gamma_C \mapsto JW_{AB}\otimes \gamma_C,
\end{equation}
where $JW_A$ is the Jordan-Wigner string over subsystem $A$, and $JW_{AB}$ is the corresponding string over subsystems $A$ and $B$. The strings preserve the fermionic anticommutation relations between subsystems.

\subsection{Projection to the Retained Space}
The full three-subsystem Hamiltonian is diagonalized, and a projection basis $V$ is formed from a selected set of eigenvectors. In the low-energy benchmark, $V$ contains the eigenvectors of the retained lowest-energy manifold. In the sector-resolved scans, a separate basis $V_i$ is instead formed from all eigenvectors belonging to energy sector $i$. Any full-space operator $O$ is then represented in the selected space by
\begin{equation}
O_P = V^\dagger O V .
\label{eq:method_operator_projection}
\end{equation}
This projection is applied to the embedded Majorana operators before they are used in the projected braid models. The same projection basis is also used for all other operators in a given calculation, so that the energy-level Majoranas, local operators, static Hamiltonian, and driven braid terms act in the same retained space.

\subsection{Projected Local Components}
In addition to the energy-level construction in Eq.~\ref{eq:method_energy_level_majoranas}, the code also constructs projected local Majorana components from the microscopic fermion operators on the relevant subsystem sites,
\begin{equation}
\Gamma_{+,P}=V^\dagger(c^\dagger+c)V,
\qquad
\Gamma_{-,P}=V^\dagger i(c^\dagger-c)V .
\end{equation}
These projected local components provide a more microscopic reference for the Majorana operator at a chosen end of a subsystem. The direct projected local-operator model uses the normalized minus component $\Gamma_{-,P}$. When this operator is compared with the corresponding energy-level Majorana, only an overall sign is allowed,
\begin{equation}
s_{\mathrm{opt}}
=
\underset{s\in\{-1,+1\}}{\operatorname{argmin}}
\left\|
\Gamma_{-,P}-s\gamma_{-}^{P}
\right\|_F .
\end{equation}
This sign alignment is used only to compare the two operator constructions; it does not allow the local operator to rotate into a different energy-level Majorana direction.

For higher-dimensional energy sectors, a single overall sign is generally insufficient. Degenerate sectors contain several independent blocks associated with different combinations of subsystem energy-level labels. A label operator is therefore constructed from the paired eigenstates of each subsystem and projected into the selected sector. Diagonalizing this projected label operator decomposes the sector into labelled blocks. Within each block $r$, the projected local operator is fitted independently to the two available energy-level Majorana components,
\begin{equation}
\Gamma_{-,P}^{(r)}
\approx
a_r\gamma_{+,P}^{(r)}
+
b_r\gamma_{-,P}^{(r)} .
\label{eq:method_block_matched_majorana}
\end{equation}
The coefficients $a_r$ and $b_r$ are continuous least-squares coefficients and are allowed to differ between blocks. The fitted blocks are then reassembled into a block-matched local operator on the full selected sector. This construction tests whether the local operator can be represented by the energy-level Majorana pair after the independent degenerate blocks have been identified. The detailed construction of the label operator and the resulting block structure is presented together with the sector-resolved analysis, and explained in the appendix \ref{app:block_label_method}.

\subsection{Normalization and Algebra Checks}
After projection, the Majorana operators are no longer assumed to satisfy the ideal algebra exactly. The projected operators are therefore checked numerically before being used in the braid. The diagnostics test Hermiticity, normalization,
\begin{equation}
\gamma_i^2 \approx I,
\end{equation}
and mutual anticommutation,
\begin{equation}
\{\gamma_i,\gamma_j\}\approx 0
\qquad (i\neq j).
\end{equation}
The matrix mismatch between the direct projected local component and the block-matched operator is also stored. These checks are important because the later braid errors should not be interpreted only as failures of the pulse protocol: they can also reflect imperfect Majorana operators after projection.


\section{Braiding Models and Pulse Protocol}
% 3.5 Braiding Models and Pulse Protocol
%   - three-subsystem junction geometry
%   - ideal four-Majorana model
%   - projected microscopic junction model
%   - projected local-operator model
%   - pulse sequence and time-dependent couplings
The braiding calculations use the optimized PMM chains as building blocks for a three-subsystem junction. The purpose of this section is to define the Hamiltonians that are driven during the braid and the common pulse sequence used for all model variants. The following section then describes how the resulting time-dependent evolution is transported and compared with the target exchange gate.

\subsection{Three-Subsystem Geometry}
The junction consists of three optimized PMM subsystems, labelled $A$, $B$, and $C$. Subsystem $A$ acts as the reference arm and supplies two Majorana operators, denoted $\gamma_0$ and $\gamma_1$. The Majorana operators to be exchanged are associated with subsystems $B$ and $C$, and are denoted $\gamma_2$ and $\gamma_3$. In this notation, the intended exchange is generated by moving the coupling of $\gamma_0$ from $\gamma_1$ to $\gamma_2$, then to $\gamma_3$, and finally back to $\gamma_1$.

All braiding models are built in the projected Hilbert space introduced in Sec.~\ref{sec:method-effective-majorana-construction}. The projection basis determines which states of the full three-subsystem Hamiltonian are retained. Within this common projected space, different choices of coupling operators can be compared directly.

In the projection scans, the driven braid terms can also be supplemented by the projected static Hamiltonian of the uncoupled subsystem background,
\begin{equation}
H_{\mathrm{static}}
=
V^\dagger\left(H_B+H_C\right)V.
\end{equation}
This term keeps the internal optimized-chain structure of subsystems $B$ and $C$ while the time-dependent junction couplings are varied. Since it is included in the same way for the model comparisons, the differences between the braid results come from the choice of driven coupling operators rather than from a different static background.

\subsection{Ideal Four-Majorana Model}
The simplest braid model uses only four Majorana operators and hand-chosen bilinear couplings. In the projected space, the time-dependent Hamiltonian is
\begin{equation}
H_{\mathrm{ideal}}(t)
=
\lambda_1(t)\, i\gamma_0\gamma_1
+
\lambda_2(t)\, i\gamma_0\gamma_2
+
\lambda_3(t)\, i\gamma_0\gamma_3 .
\label{eq:method_ideal_braid_hamiltonian}
\end{equation}
This model is used as a reference calculation. Since the couplings are written directly as Majorana bilinears, it isolates the braid protocol itself from the additional complications of microscopic junction operators and imperfect projected Majoranas.

\subsection{Projected Microscopic Junction Model}
To connect the braid more directly to the optimized dot-chain Hamiltonian, the ideal bilinears can be replaced by microscopic junction operators. The junction between subsystems $A$ and $B$ is constructed from ordinary hopping and pairing terms between the endpoint dots,
\begin{equation}
H^{\mathrm{junc}}_{AB}
=
-t_{\mathrm{j}}
\left(c_A^\dagger c_B+c_B^\dagger c_A\right)
+
\Delta_{\mathrm{j}}
\left(c_A c_B+c_B^\dagger c_A^\dagger\right),
\label{eq:juncHam}
\end{equation}
with an analogous operator $H^{\mathrm{junc}}_{AC}$ for the $A$--$C$ junction. These full-space junction operators are projected into the retained low-energy space,
\begin{equation}
T_{AB}=V^\dagger H^{\mathrm{junc}}_{AB}V,
\qquad
T_{AC}=V^\dagger H^{\mathrm{junc}}_{AC}V.
\label{eq:method_projected_junctions}
\end{equation}
The corresponding projected microscopic braid Hamiltonian is then
\begin{equation}
H_{\mathrm{junc}}(t)
=
\lambda_1(t)\,T_A
+
\lambda_2(t)\,T_{AB}
+
\lambda_3(t)\,T_{AC},
\label{eq:brajunc}
\end{equation}
where $T_A=i\gamma_0\gamma_1$ fixes the initial pairing inside subsystem $A$. This model tests whether the physical junction couplings reproduce the desired Majorana exchange after projection.

\subsection{Projected Local-Operator Model}
A second microscopic comparison keeps the bilinear braid structure but replaces the ideal exchanged Majoranas by projected local Majorana components. For example, on the relevant endpoint of subsystem $B$ one constructs
\begin{equation}
\Gamma_{B,-}
=
V^\dagger i(c_B^\dagger-c_B)V,
\end{equation}
and similarly for subsystem $C$. After normalization, these local projected operators define $\gamma_{2,\mathrm{loc}}$ and $\gamma_{3,\mathrm{loc}}$. The local-operator braid Hamiltonian is
\begin{equation}
H_{\mathrm{loc}}(t)
=
\lambda_1(t)\, i\gamma_0\gamma_1
+
\lambda_2(t)\, i\gamma_0\gamma_{2,\mathrm{loc}}
+
\lambda_3(t)\, i\gamma_0\gamma_{3,\mathrm{loc}} .
\label{eq:method_local_operator_braid}
\end{equation}
This model is useful because it sits between the ideal and fully microscopic descriptions. The projected microscopic model first projects the full junction operator, while the projected local-operator model first projects local Majorana components and then forms bilinears from them. It therefore keeps a clear Majorana-bilinear form, but the operators being coupled are obtained from projected local fermionic operators rather than only from energy-level parity pairs.

\subsection{Block-Matched Local-Operator Model}
The sector-resolved scans also use a block-matched local-operator model. It has the same bilinear form as Eq.~\ref{eq:method_local_operator_braid}, but replaces the direct projected local operators by the block-matched operators defined in Eq.~\ref{eq:method_block_matched_majorana}. The labelled blocks are fitted independently and then reassembled before the braid Hamiltonian is constructed. This model tests whether resolving the internal degeneracy structure of a sector improves the braid generated from the local channel.

\subsection{Pulse Sequence}
The same pulse sequence is used for each braid model. To avoid confusing the braid amplitudes with the superconducting pairing parameters $\Delta_i$, the time-dependent braid couplings are denoted by $\lambda_i(t)$. The coupling envelope is a smooth pulse constructed from two sigmoid functions,
\begin{equation}
\lambda(t;T_p)
=
\lambda_{\min}
+
(\lambda_{\max}-\lambda_{\min})
\frac{1}{1+\exp[-sP_+(t;T_p)]}
\frac{1}{1+\exp[sP_-(t;T_p)]},
\label{eq:method_lambda_pulse}
\end{equation}
where
\begin{equation}
P_+(t;T_p) = t-T_p+w/2,
\qquad
P_-(t;T_p) = t-T_p-w/2.
\end{equation}
where $T_p$ is the pulse center, $w$ is the pulse width, and $s$ controls the steepness of the rise and fall. The three braid couplings are then chosen as
\begin{equation}
\lambda_1(t)
=
\lambda(t;0)+\lambda(t;T)-\lambda_{\min},
\qquad
\lambda_2(t)
=
\lambda(t;T/3),
\qquad
\lambda_3(t)
=
\lambda(t;2T/3).
\label{eq:method_braid_pulses}
\end{equation}
Thus the $A$-arm coupling is active at the beginning and end of the cycle, while the $A$--$B$ and $A$--$C$ couplings are activated in sequence during the middle of the protocol. In the numerical calculations used here, the total braid time is set to $T=1$, with $\lambda_{\max}=1$, $\lambda_{\min}=0$, pulse width $w=T/3$, and steepness $s=20/w$.

At each time step, the Hamiltonian for the chosen model is assembled from the same three time-dependent coefficients. The instantaneous spectrum is monitored along the path, and the isolated low-energy band is then transported using the Kato procedure described in the next section.

\section{Kato Transport and Braid Validation}
% 3.6 Kato Transport and Braid Validation
%   - numerical Kato propagation
%   - transported bands used in the calculations
%   - target exchange gate
%   - operator-action checks:
%     gamma_2 -> -gamma_3,
%     gamma_3 -> gamma_2
%   - parity-block leakage
%   - odd/even target-gate errors
%   - energy-level target vs projected-local target
After a braid Hamiltonian has been defined, the remaining task is to compute the unitary generated by the adiabatic path and to check whether it implements the desired Majorana exchange. The calculation is performed in the projected Hilbert space, but the transported subspace can be smaller than the full projection space. This section describes the transported bands used in the calculations, how the Kato evolution is computed, and which diagnostics are used to compare the resulting unitary with the target braid.

\subsection{Transported Bands}
In the low-energy benchmark, the transported subspace is the isolated four-dimensional lowest-energy manifold. Its gap to the remaining projected states is monitored throughout the braid path.

In the sector-resolved scans, each energy sector is projected and tested independently. Activating the braid Hamiltonian splits the initially degenerate sector into a lower and an upper band of equal dimension. The Kato calculation transports the lower band, so that for a sector projection of dimension $d_{P_i}$ the transported dimension is fixed to
\begin{equation}
d_{T_i}=\frac{d_{P_i}}{2}.
\label{eq:method_sector_transport_dimension}
\end{equation}
The spectral gap between these two bands is monitored along the path. The existence of this isolated lower band makes the transport well defined, while the final target comparison determines whether the transported unitary actually performs the intended exchange.

\subsection{Numerical Kato Transport}
The braid path is discretized into time points $t_0,\ldots,t_N$. At each time step, the Hamiltonian is diagonalized and the projector onto the transported band is constructed,
\begin{equation}
P(t_\ell)
=
\sum_{a=1}^{d_T}
\ket{\psi_a(t_\ell)}\bra{\psi_a(t_\ell)} .
\end{equation}
The Kato generator is approximated from consecutive projectors,
\begin{equation}
K(t_\ell)
=
P(t_\ell)\dot{P}(t_\ell)
-
\dot{P}(t_\ell)P(t_\ell),
\qquad
\dot{P}(t_\ell)
\approx
\frac{P(t_{\ell+1})-P(t_\ell)}{\Delta t}.
\end{equation}
The transport unitary is updated as
\begin{equation}
U_K(t_{\ell+1})
=
\exp[-\Delta t\,K(t_\ell)]U_K(t_\ell),
\qquad
U_K(t_0)=I .
\label{eq:method_kato_update}
\end{equation}
This convention matches the numerical implementation and gives the geometric transport of the selected subspace along the braid path. The instantaneous energies and pulse amplitudes are stored at the same time, so that the quality of the transported band can be checked together with the final braid unitary.

\subsection{Target Exchange Gate}
The target unitary for exchanging $\gamma_2$ and $\gamma_3$ is taken to be
\begin{equation}
U_{\mathrm{target}}
=
\exp\left(
-\frac{\pi}{4}\gamma_2\gamma_3
\right).
\label{eq:method_target_exchange_gate}
\end{equation}
This convention corresponds to the exchange action
\begin{equation}
\gamma_2\mapsto -\gamma_3,
\qquad
\gamma_3\mapsto \gamma_2,
\end{equation}
up to the overall sign convention chosen for the Majorana operators. Since a global phase of the transported unitary is physically irrelevant, comparisons with the target gate are made after aligning the overall phase. In practice, the reported gate error is a Frobenius-norm distance between the transported unitary and the phase-aligned target unitary, restricted to the initial transported basis.

\subsection{Operator-Action Checks}
The first validation step checks the induced action on the Majorana operators directly. For each model, the transported unitary is applied as
\begin{equation}
\gamma_i'
=
U_K^\dagger \gamma_i U_K.
\end{equation}
The resulting operators are compared with the expected single-exchange map,
\begin{equation}
\gamma_2' \approx -\gamma_3,
\qquad
\gamma_3' \approx \gamma_2,
\qquad
\gamma_0' \approx \gamma_0,
\qquad
\gamma_1' \approx \gamma_1.
\end{equation}
The mismatch is measured using a normalized Frobenius norm,
\begin{equation}
\|A\|_{\mathrm{norm}}
=
\frac{\|A\|_F}{\sqrt{d}},
\end{equation}
where $d$ is the dimension of the matrix being compared. These checks are useful because they test the braid as an operator transformation, rather than only as a matrix acting on a chosen basis.

\subsection{Parity-Resolved Gate Checks}
The transported unitary is also analyzed in a parity basis. The total parity operator is projected into the initial transported space and diagonalized, separating the unitary into odd- and even-parity blocks. The off-block leakage is defined from the norm of the odd-to-even and even-to-odd blocks,
\begin{equation}
\mathcal{L}_{\mathrm{parity}}
=
\|U_{oe}\|
+
\|U_{eo}\|.
\end{equation}
A small value indicates that the braid approximately preserves fermion parity inside the transported manifold.

After the parity blocks have been separated, each block is compared with the corresponding block of the target exchange gate in Eq.~\ref{eq:method_target_exchange_gate}. This produces separate odd- and even-sector target-gate errors. Reporting the parity blocks separately is useful because the same Majorana exchange can appear with different matrix representations in the two parity sectors, while still describing the same physical braid.

\subsection{Energy-Level and Projected-Local Targets}
The final comparison distinguishes between two possible choices of target Majoranas. The energy-level target uses the Majorana operators constructed from even-odd parity pairs, as described in Sec.~\ref{sec:method-effective-majorana-construction}. The projected-local target instead uses the normalized projected local operators obtained from microscopic combinations such as $i(c^\dagger-c)$. These two targets need not be identical after projection, especially when more excited states are retained or when the optimized Majorana operators are not perfectly local.

For this reason, the physical braid is compared in several ways: against the energy-level target, against the projected-local target, and against the ideal reference braid. The mismatch between the two target constructions is also recorded. This separation is important for interpreting the results. If the physical braid disagrees with the energy-level target but agrees with the projected-local target, the issue may be the identification of the effective Majorana operators rather than the adiabatic pulse itself. Conversely, if both target comparisons fail, the projected braid Hamiltonian is not implementing the desired exchange within the chosen transported subspace.
